\section*{AI Acknowledgment}

This work began as an exploration of how Hawking radiation within a black hole might influence its internal structure. The process of formalizing these ideas and predicting their implications was significantly aided by AI-assisted tools. While the underlying questions originate from human intuition and inquiry, AI contributed to refining, organizing, and extending the theoretical framework.

Specifically, the AI system assisted in:
\begin{itemize}
    \item Structuring and systematically developing theoretical concepts.
    \item Assisting with LaTeX document preparation and mathematical formalization.
    \item Suggesting refinements to definitions, notation, and consistency in presentation.
    \item Identifying potential gaps and logical dependencies within the proposed framework.
    \item Proposing lines of inquiry and highlighting where additional theoretical justification is required.
\end{itemize}

This paper does not claim to present a definitive theory but rather an exploration of an interesting question. The AI-assisted process led to a framework that extends beyond the author's ability to fully evaluate, making it an exercise in speculative theorization rather than confirmed physics. The hope is that this formalization may inspire further rigorous investigation by those with deeper expertise in quantum gravity and black hole physics.

All intellectual contributions, critical reasoning, and final theoretical judgments remain the responsibility of the human author. The AI served as a tool to enhance clarity, organization, and technical formulation, but the responsibility for correctness, validity, and originality of the work lies solely with the author.
